Practical Optional Types for Clojure

### 2015-02-27 overview.tex
formatting

\paragraph{HMap dispatch} The flexibility of \clj{isa?} is key to the generality of multimethods. 
We can dispatch on the \clj{:op} key 
of our HMap AST \clj{Expr}.
Since keywords are functions that look themselves up in their argument, we simply
use \clj{:op} as the dispatch function.

\begin{exmp}
\inputminted[firstline=5,lastline=18]{clojure}{code/demo/src/demo/eg5.clj}
\label{example:incmap}
\end{exmp}

@@

Now we can simulate multiple dispatch by dispatching on
a vector containing the class of both arguments. \clj{open}
takes two arguments which can be strings or files and returns
a new file that concatenates their paths.

\begin{exmp}
\inputminted[firstline=6,lastline=22]{clojure}{code/demo/src/demo/eg7.clj}
\end{exmp}

@@

The final example combines everything we will cover for the rest of the paper:
multimethod dispatch, reflection resolution via type hints, Java method
and constructor calls, conditional and exceptional flow reasoning,
and HMaps.

\begin{exmp}
\inputminted[firstline=6,lastline=20]{clojure}{code/demo/src/demo/eg8.clj}
\end{exmp}

>>>>

\paragraph{HMap dispatch} The flexibility of \clj{isa?} is key to the generality of multimethods. 
In example~\ref{example:incmap} we
dispatch on the \clj{:op} key 
of our HMap AST \clj{Expr}.
Since keywords are functions that look themselves up in their argument, we simply
use \clj{:op} as the dispatch function.

\begin{figure}
\begin{exmp}
\inputminted[firstline=5,lastline=18]{clojure}{code/demo/src/demo/eg5.clj}
\label{example:incmap}
\end{exmp}
\end{figure}

@@

Example~\ref{example:multidispatch}
simulates multiple dispatch by dispatching on
a vector containing the class of both arguments. \clj{open}
takes two arguments which can be strings or files and returns
a new file that concatenates their paths.

\begin{figure}
\begin{exmp}
\inputminted[firstline=6,lastline=22]{clojure}{code/demo/src/demo/eg7.clj}
\label{example:multidispatch}
\end{exmp}
\end{figure}

@@

Example~\ref{example:final}
combines everything we will cover for the rest of the paper:
multimethod dispatch, reflection resolution via type hints, Java method
and constructor calls, conditional and exceptional flow reasoning,
and HMaps.

\begin{figure}
\begin{exmp}
\inputminted[firstline=6,lastline=20]{clojure}{code/demo/src/demo/eg8.clj}
\label{example:final}
\end{exmp}
\end{figure}
